Think deep for reef resilience

### 2025-08-12 paper/paper_draft.qmd
Add comment for @eco-ben :)

: Information for each GCM used in this investigation including Equilibrium Climate
Sensitivity (ECS) value, interpreted relative severity and where results are individual GCM
results are found. GCMs in context with assessed plausible ranges of ECS values are
displayed in [@sfig-ecs]. ACCESS-ESM1-5 has an ECS closest to the midpoint of the
very-likely ECS range and was taken as an intermediate model with results displayed in the
main text. ECS values obtained from: [@sentman2025; @grose2023; @seland2020; @ziehn2020;
@wyser2020].
:::

@@

**\[TODO - rewrite/expand paragraphs below for flow\]**
As ADRIA - CoralBlox has not been
validated at the GBR-wide scale, we aim to assess the relative influence of reef
characteristics on resilience under future change rather than provide spatially explicit
predictions of reef outcomes into the future. Using this approach we suggest that median
reef depth is an important factor for reef resilience under thermal stress. Improvements in
remote sensing approaches for broad scale bathymetry measurement, and understanding of how
depth impacts experienced thermal stress on reefs will further enhance investigations of
depth as a critical factor for reef resilience. Additional analyses could build on the
findings of this study by assessing the impacts of prioritising reef depth in reef
restoration decision making. The ADRIA platform is developed as a modelling tool to
incorporate multi-criteria decision analysis (MCDA) and ecosystem scenario modelling into
reef restoration decision support. This platform allows for different intervention
priorities to be dynamically targetted in decision making, while modelling the evolving
outcomes as a result of interventions. The capability of ADRIA-CoralBlox could be further
expanded by incorporating the impacts of waves, cyclones, CoTS and currents into future
resilience investigations [@lin2023; @mcclanahan2005; @grimaldi2023; @grimaldi2022;
@liu2024]. Additionally, the investigation could be enhanced by incorporating ocean
acidification projections into analyses of coral carbonate budgets [@eyre2018].

>>>>

: Information for each GCM used in this investigation including Equilibrium Climate
Sensitivity (ECS) value, interpreted relative severity and where results are individual GCM
results are found. GCMs in context with assessed plausible ranges of ECS values are
displayed in [@sfig-ecs]. ACCESS-ESM1-5 has an ECS closest to the midpoint of the
very-likely ECS range and was taken as an intermediate model with results displayed in the
main text. ECS values obtained from: [@sentman2025; @grose2023; @seland2020; @ziehn2020;
@wyser2020]. **\[TI: Ben, I would add this to the table directly in the ECS value column
(ECS value and source). The table should also be ordered by ECS value (high to low)\]**
:::

@@

**\[TODO - rewrite/expand paragraphs below for flow\]** As ADRIA-CoralBlox has not been
validated at the GBR-wide scale, we aim to assess the relative influence of reef
characteristics on resilience under future change rather than provide spatially explicit
predictions of reef outcomes into the future. Using this approach we suggest that median
reef depth is an important factor for reef resilience under thermal stress. Improvements in
remote sensing approaches for broad scale bathymetry measurement, and understanding of how
depth impacts experienced thermal stress on reefs will further enhance investigations of
depth as a critical factor for reef resilience. Additional analyses could build on the
findings of this study by assessing the impacts of prioritising reef depth in reef
restoration decision making. The ADRIA platform is developed as a modelling tool to
incorporate multi-criteria decision analysis (MCDA) and ecosystem scenario modelling into
reef restoration decision support. This platform allows for different intervention
priorities to be dynamically targetted in decision making, while modelling the evolving
outcomes as a result of interventions. The capability of ADRIA-CoralBlox could be further
expanded by incorporating the impacts of waves, cyclones, CoTS and currents into future
resilience investigations [@lin2023; @mcclanahan2005; @grimaldi2023; @grimaldi2022;
@liu2024]. Additionally, the investigation could be enhanced by incorporating ocean
acidification projections into analyses of coral carbonate budgets [@eyre2018].
